The Calibration Reference Data System

### 2015-10-04 docs/paper/crds.tex
fixed a bunch of figure issues
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@2123 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

The system that was used for the Hubble Space Telescope (HST) was called the
Calibration Database System (CDBS). It was used successfully for many
years. The experience with it revealed that there were some limitations that
proved to constrain its capabilities, and as a result, a newer system that
removed these constraints was sought. We will briefly describe the design of
CDBS at a high level and the constraints that it posed. This provides the
necessary background for discussing the design goals of CRDS.

>>>>

The system that was used for the Hubble Space Telescope (HST) was called the
Calibration Database System (CDBS,  
\citealt{1994Cox,1997Lubow,1998Cox,1997hstinternal,2004Swam}). It was used successfully for many years (with some design changes documented in the 
cited references). The experience with it revealed that there were some limitations that
proved to constrain its capabilities, and as a result, a newer system that
removed these constraints was sought. We will briefly describe the design of
CDBS at a high level and the constraints that it posed. This provides the
necessary background for discussing the design goals of CRDS.
